Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-13 aistats.tex
finished the pass on section 5

\subsection{Quadratic Case}
\rlp{make it multivariate, with a reference to \citep{bach2013nonstronglyconvex}?}
As another reference point, let us consider the case $\logpart(\nat) = \half \norm{\nat}_2^2$.
For instance, this is the log-partition of a Gaussian with variance $1$ and unknown mean 
\[ \cX=\real,\quad \nu(dx) = \exp(\half[-x^2])dx,\quad T(X)=X.\]
Then $\conj(\meanp) = \half \norm{\meanp}_2^2$ as well, and both Bregman divergences are squared $\ell^2$ distances:
\begin{align}
	\bregmanconj(\meanp^* ; \meanp) = \half \norm{\meanp^* -  \meanp }_2^2  \; .
\end{align}
Thanks to the independence of samples, we can break down the MLE into individual point's contributions
\begin{align}
	\expect{\half \norm{\m^* -  \inv{n}  \smallsum_i T_i}_2^2}
	=\frac{\Var(T)}{2n}
	=\frac{1}{2n}
\end{align}
Adding a reference mean $\m_0$ to get the MAP yields to
\begin{align}
	\expect{\bregmanconj(\meanp^*; \MAPm)}
	&= \frac{n \Var(T) +  n_0^2 \norm{\m^* -  \m_0}^2}{2(n+n_0)^2}.
	%\\ &= O\left(\frac{\Var(T)}{n} \right) + O\left(\frac{\norm{\m^* -  \m_0}^2}{n^2} \right)
	\label{eq:MAP_quadratic}
\end{align}
In both cases, we have a variance term in $O(n^{-1})$ and a bias term in $O(n^{-2})$. Ideally, such result should also similarly for arbitrary exponential families.
If we make restrictive assumptions on the log-partition function, we can relate $\bregmanconj$ to a norm or a quadratic.

@@

{\bf If $\conj$ is $L$-smooth} (e.g. $\logpart$ is $\frac{1}{L}$-strongly convex \citep{kakade2009duality}), then
\begin{align}
    \bregmanconj(\m^* ; \m)
    \leq \frac{L}{2} \norm{\m^* - \m}^2
\end{align}
so $\bregmanconj$ is upper bounded by a quadratic, and we get~\eqref{eq:MAP_quadratic} as an upper bound.
Note that it is also possible to get (more complex) upper bounds under restricted notions of strong-convexity \citep{negahban2012unified}.
\TODO{connection with optim smooth rate.}

\subsection{Locally Quadratic Case}
\textcolor{red}{Check this! In our case, since we assume $A$ and $A^*$ to be strictly convex,}
all Bregman divergences are locally quadratic.
Under some assumptions, like self-concordance of $\conj$ \citep[Ch.4.1]{nesterov2003introductory}, we can quantify when this quadratic behavior kicks in.
\begin{proposition}
Let $\conj:\cM\rightarrow \real$ be a self-concordant convex function, $\m, \m^* \in\cM$ and $\mF = \nabla \conj(\m^*)$. Then%\footnote{$0.21$ is the value of $x$ such that $x^2 \geq -\frac{x}{1-x} - \log(1 - \frac{x}{1-x})$}
\aligns{
	\norm{\m^*-\m}_{\mF} < 0.21 
	\implies
	\bregmanconj(\m^*,\m) \leq \norm{\m^*-\m}_{\mF}^2
}
\end{proposition}
Proof in the appendix.
We know that $\conj$ is self-concordant when $T$ is 1-dimensional and $\logpart$ is self-concordant.
This is true for
exponential distributions,
Gaussians with known mean,
Laplace with known mean,
Pareto with known minimum value,
or Weibull with known shape $k$. 
The entropy is also self-concordant when $T$ lives in a compact \citep{bubeck2015entropic}.

With some more work, it is possible to get a wealth of results under this assumption.
For instance \citet{ostrovskii2021finite} characterizes the number of samples needed to reach this quadratic behavior for arbitrary parametric models, under the assumptions of self-concordance, or pseudo self-concordance \citep{bach2010self}.
Or in the world of exponential families, \citet{kakade2010learning} assumes a local bound on all higher order moments of $\logpart$ in $\nat^*$, to quantify when $\logpart$ can be sandwiched between quadratics in $\nat$, but this does not directly translate into quadratics in $\m$.

@@

\citet{anastasiou2017bounds} and
\citet{marteauferey2019beyond})
\fdk{
We know that if the problem is strongly convex (in $\norm{\cdot}_2$), averaged SGD achieves $O(1/n)$ rate.
[Robust stochastic approximation approach to stochastic programming]. (The paper uses a bounded stochastic gradient assumption, but can be relaxed to bounded variance instead.) However, strong-convexity in the Euclidean norm is not strictly necessary to find an algorithm with convergence rate of $O(1/n)$, as shown by [Non-strongly-convex smooth stochastic approximation with convergence rate O(1/n)] for linear and logistic regression. Their proof techniques based on self-concordance have been extended to other setting, [Finite-sample analysis of M-estimators using self-concordance, Learning Exponential Families in High-Dimensions: Strong Convexity and Sparsity].
The same tools are used in statistics, and evething essentially boils down to controlling how different we are from a Gaussian rv, that we're going to get by the CLT, like [Bounds for the normal approximation of the maximum likelihood estimator, Anastasiou].
}

\subsection{Bias-Variance Decomposition} % DS: Arrived here
In both examples (add link), the upper bound takes the form $O(\inv{n}) + O(\frac{\text{bias}}{n^2})$, reminding us of the bias-variance decomposition. In fact, it is possible to write such a decomposition for any Bregman divergence
Let $\tilde \theta_n := \expecti{\hat \theta_n}$ be the expectation of the MAP in primal space, and $\tilde \m_n = \nabla \logpart(\tilde \theta_n )$ be the corresponding mean parameter.
As described by \citet[Theorem 0.1]{pfau2013generalized}, the  expected Bregman decomposes like
\begin{align}
	\expect{\bregmanconj(\m^* ; \hat \m_n)}
	&= {\bregmanconj(\m^* ; \tilde \m_n)}
	+ {\expect{\bregmanconj(\tilde \m_n ; \MAPm)}}
	\label{eq:primal_pivot}
\end{align}

\textbf{Remark:} In this decomposition, the primal expectation $\expect{\hat \theta_n}$ is taking the role of pivot / reference point. An estimator will be unbiased if its primal expectation is non-zero.
This is not true for the MLE. In fact for the gaussian variance MLE, the bias decreases like ${\bregmanconj(\m^* ; \tilde \m_n)} \leq \frac{2}{n(n-2)}$.
A contrario, the MLE is unbiased wrt the dual parameter, but the decomposition there is not clean.

\paragraph{Illustrations.}
We show these decompositions for $\cN(0,\sigma^2)$ in Figure~\ref{fig:variance_decomposition} and  $\cN(\mu, \sigma^2)$ in Figure~\ref{fig:gaussian_decomposition}.
In particular for $\cN(\mu, \sigma^2)$, we illustrate the characters featured in these decompositions $\hat \m_n^\text{MLE},\hat \m_n^\text{MAP},\m_n,\tilde \m_n, \m^*$ and $\m_0$ (and corresponding primal parameters)  in Figure~\ref{fig:bias-variance-numerical}. \rlp{Tune figures.}

@@

\subsection{Gaussian Variance}
A core example of this paper is a centered gaussian with unknown variance $\cN(0,\sigma^2)$.
The density is	$p(x) = \inv{\sqrt{2\pi \sigma^2}} e^{-\frac{x^2}{2 \sigma^2}}$.
Defining $T(X)=X^2$ as the sufficient statistic, we get natural parameter $\nat = -\inv{2 \sigma^2} <0$, and mean parameter $\m=\E[T(X)] = \sigma^2 >0$.
Mean and natural parameters are roughly inverse of each other $\nat = -\inv{2 \m}$.
Now we can match the log-likelihood with the exponential family template to get the log-partition function, and taking the conjugate to find the entropy
\begin{align}
	\logpart (\nat) &= - \half \log(-\nat)  + \half \log(\pi) \\
	\conj(\m) &= \half\left( -\log(\m) + \log\frac{\pi}{2} - 1 \right) \; .
\end{align}
Both the log-partition and  the entropy are roughly negative logarithm $z\mapsto - \log(z)$.
It means the conjugate prior is the exponential family with sufficient statistic $(\nat, \log(-\nat) )$, eg a negative Gamma distribution.
It also means $\bregman$ and $\bregmanconj$ have the same shape
\begin{align}
	\bregmanconj( \m_*; \m_n)
	&= \half \left ( \frac{\m_*}{ \m_n} - 1 - \log  \frac{\m_*}{ \m_n} \right) \\
	\bregman( \nat_n; \nat_* )
	&=  \half \left ( \frac{ \nat_n}{\nat_*} - 1 - \log  \frac{ \nat_n}{\nat_*} \right) \; .
\end{align}
In other words, this divergence measures the discrepancy between the ratio $\frac{ \nat_n}{\nat_*} =  \frac{\m_*}{ \m_n}  $ and $1$ via the function $\phi$
\begin{align}
	\phi(z) := \half (z - 1 - \log(z))
\end{align}
illustrated in Figure~\ref{fig:phi}.
Below we report upper bounds on the expected value of this divergence for the MLE and the MAP.

@@

@@

For the MAP, we get an upper bound thanks to the inequality $ - \log(z) \leq \inv{z} - 1$ which implies
\begin{align}
	\label{eq:log_bound}
	\phi(z) \leq \half (z + \inv{z}) - 1 = \frac{(z-1)^2}{2 z} \; .
\end{align}

\begin{theorem}[MAP Bound]
 For $n\in \naturalnumbers$, let us  define
 \begin{align}
	b_n = \frac{(1 + \inv{n_0} - \frac{\m_0}{\m^*})^2}{2 (\frac{\m_0}{\m^*}+\frac{(n-2)_+}{n_0})(1 + \frac{n}{n_0} )} \; .
 \end{align}
The expected suboptimality of the MAP of $\cN(0,\m^*)$ with prior hyper-parameters $(n_0,\m_0)$ is
 \begin{equation}
	\expect{\bregmanconj( \m_*; \hat \m_n^\mathrm{MAP})}
	\leq \begin{cases}
		\inv{2(n_0+1)}  +  b_1 \ \text{if}\ n=1,\\
		\frac{1}{n_0 \frac{\m_0}{\m^*} +n-2} + b_n \ \text{if}\ n\geq 2
	\end{cases}
	\label{eq:MAP_rate}
\end{equation}
\end{theorem}

This inequality highlights a clear variance-bias decomposition.
In particular, there is no bias term when $\frac{\m_0}{\m^*} =1 + \inv{n_0} $, which happens when the prior is slightly larger than the ground truth.  For instance, when $n_0=1$, it encourages us to set $\m_0 = 2 \m^*$. This correlates well with numerical observations.
Remark that the variance term is not asymptotically tight as the log-inequality we used \eqref{eq:log_bound} is not quadratically tight around $1$. We are basically losing a factor 2 compared to $1/2n$.

@@

We now show how MAP can be interpreted as stochastic mirror descent (SMD).
This means that 1. we may obtain a convergence rate for MAP from an optimization analysis, and 2. any insights gained from the MAP may inform further design and analysis of SMD.
We then review the assumptions of relative smoothness, useful to deal with non-smooth functions, before investigating 3 analysis of SMD with the MAP.
\rlp{mention that examples have so far been lacking for relative SMD.}

@@

\subsubsection{Bounded Optimality Gap}
Inspired by \citet{loizou2021stochastic}, \citet{dorazio2021stochastic} explores the hypothesis
\alignn{
\min_\nat f(\nat) - \expect[X]{\min_\nat f_X(\nat)} \leq C 
\label{eq:dorazio}
}
where $f_X$ is a stochastic estimate of $f = \expecti{f_X}$. In our case $f_X(\nat) = - \log p(X\cond \nat)$.
In words, this is lower bounding the expectation of the minimum of these stochastic estimates.
For probabilistic models, such a bound is finite as soon as the model cannot give infinite density to any data point $x$.
This holds for instance for discrete distributions 
-- $f_x\geq 0$ because the probability mass is upper bounded by $1$ -- 
but it rules out  many families.
For normal distributions set $\mu=x$ and $\sigma^2 \rightarrow 0$ to get $p(x\cond \nat) \rightarrow +\infty$. 
For gamma, set $\alpha = \beta x$ and $\beta \rightarrow +\infty$.
For beta, set $\alpha=\beta \frac{x}{1-x}$ and $\beta \rightarrow +\infty$.
 Other examples include inverse Gaussians, log-normal, gamma, inverse gamma.

>>>>

\subsection{Quadratic Case}
\rlp{make it multivariate, with a reference to \citep{bach2013nonstronglyconvex}?}
As another reference point, let us consider the case $\logpart(\nat) = \half \norm{\nat}_2^2$.
For instance, this is the log-partition of a Gaussian with variance $1$ and unknown mean 
\[ \cX=\real,\quad \nu(dx) = \exp(\half[-x^2])dx,\quad T(X)=X.\]
Then $\conj(\meanp) = \half \norm{\meanp}_2^2$ as well, and both Bregman divergences are squared $\ell^2$ distances:
\begin{align}
	\bregmanconj(\meanp^* ; \meanp) = \half \norm{\meanp^* -  \meanp }_2^2  \; .
\end{align}
Thanks to the independence of samples, we can break down the MLE into individual point's contributions
\begin{align}
	\expect{\half \norm{\m^* -  \inv{n}  \smallsum_i T_i}_2^2}.
	=\frac{\Var(T)}{2n}
	=\frac{1}{2n}
\end{align}
Adding a reference mean $\m_0$ to get the MAP yields to
\begin{align}
	\expect{\bregmanconj(\meanp^*; \MAPm)}
	&= \frac{n \Var(T) +  n_0^2 \norm{\m^* -  \m_0}^2}{(n+n_0)^2}.
	%\\ &= O\left(\frac{\Var(T)}{n} \right) + O\left(\frac{\norm{\m^* -  \m_0}^2}{n^2} \right)
	\label{eq:MAP_quadratic}
\end{align}
In both cases, we have a variance term in $O(n^{-1})$ and a bias term in $O(n^{-2})$. Ideally, such result should also similarly for arbitrary exponential families.
If we make restrictive assumptions on the log-partition function, we can relate $\bregmanconj$ to a norm or a quadratic.

@@

{\bf If $\conj$ is $L$-smooth} (e.g. $\logpart$ is $\frac{1}{L}$-strongly convex \citep{kakade2009duality}), then
\begin{align}
    \bregmanconj(\m^* ; \m)
    \leq \frac{L}{2} \norm{\m^* - \m}^2
\end{align}
so $\bregmanconj$ is upper bounded by a quadratic, and we get~\eqref{eq:MAP_quadratic} as an upper bound.
\TODO{connection with optim smooth rate.}

\subsection{Locally Quadratic Case}
\textcolor{red}{Check this! In our case, since we assume $A$ and $A^*$ to be strictly convex,}
all Bregman divergences are locally quadratic.
Under some assumptions, like self-concordance of $\conj$ \citep[Ch.4.1]{nesterov2003introductory}, we can quantify when this quadratic behavior kicks in.
\begin{proposition}
Let $\conj:\cM\rightarrow \real$ be a self-concordant convex function, $\m, \m^* \in\cM$ and $\mF = \nabla \conj(\m^*)$. Then%\footnote{$0.21$ is the value of $x$ such that $x^2 \geq -\frac{x}{1-x} - \log(1 - \frac{x}{1-x})$}
\aligns{
	\norm{\m^*-\m}_{\mF} < 0.21 
	\implies
	\bregmanconj(\m^*,\m) \leq \norm{\m^*-\m}_{\mF}^2
}
\end{proposition}
We know that $\conj$ is self-concordant when $T$ is 1-dimensional and $\logpart$ is self-concordant.
This is true for
exponential distributions,
Gaussians with known mean,
Laplace with known mean,
Pareto with known minimum value,
or Weibull with known shape $k$. 
The entropy is also self-concordant when $T$ lives in a compact \citep{bubeck2015entropic}.

\citet{kakade2010learning} assumes a bound similar to self concordance, but only at $\nat^*$ and on all higher order moments. They quantify when $\logpart$ starts behaving quadratically, but their rate does not directly apply yield a norm on $\m$.

@@

\TODO{Incorporate this content} ( about \citet{ostrovskii2021finite} as well as
\citet{anastasiou2017bounds} and
\citet{marteauferey2019beyond})
\fdk{
We know that if the problem is strongly convex (in $\norm{\cdot}_2$), averaged SGD achieves $O(1/n)$ rate.
[Robust stochastic approximation approach to stochastic programming]. (The paper uses a bounded stochastic gradient assumption, but can be relaxed to bounded variance instead.) However, strong-convexity in the Euclidean norm is not strictly necessary to find an algorithm with convergence rate of $O(1/n)$, as shown by [Non-strongly-convex smooth stochastic approximation with convergence rate O(1/n)] for linear and logistic regression. Their proof techniques based on self-concordance have been extended to other setting, [Finite-sample analysis of M-estimators using self-concordance, Learning Exponential Families in High-Dimensions: Strong Convexity and Sparsity].
The same tools are used in statistics, and evething essentially boils down to controlling how different we are from a Gaussian rv, that we're going to get by the CLT, like [Bounds for the normal approximation of the maximum likelihood estimator, Anastasiou].
}

\subsection{Bias-Variance Decomposition} 
In both examples \textcolor{red}{(add link)}, the upper bound takes the form $O(\inv{n}) + O(\frac{\text{bias}}{n^2})$, reminding us of the bias-variance decomposition. In fact, such a decomposition exists for any Bregman divergence.
Let $\tilde \theta_n := \expecti{\hat \theta_n}$ be the expectation of the MAP in primal space, and $\tilde \m_n = \nabla \logpart(\tilde \theta_n )$ be its corresponding mean parameter.
As described by \citet[Theorem 0.1]{pfau2013generalized}, the  expected Bregman decomposes into
\begin{equation}
	\expect{\bregmanconj(\m^* ; \hat \m_n)} = {\bregmanconj(\m^* ; \tilde \m_n)}
	+ {\expect{\bregmanconj(\tilde \m_n ; \MAPm)}}
	\label{eq:primal_pivot}
\end{equation}

\textbf{Remark:} In this decomposition, the primal expectation $\expect{\hat \theta_n}$ is taking the role of pivot / reference point. An estimator will be unbiased if its primal expectation is non-zero.
However, this is not true for the the gaussian variance MLE, where the bias decreases like ${\bregmanconj(\m^* ; \tilde \m_n)} \leq \frac{2}{n(n-2)}$.
A contrario, the MLE is unbiased wrt the dual parameter, but the decomposition there is not clean.

\paragraph{Illustrations.}
We plot the bias-variance decompositions for $\cN(0,\sigma^2)$ (Figure~\ref{fig:variance_decomposition}) and  $\cN(\mu, \sigma^2)$ (Figure~\ref{fig:gaussian_decomposition}).
Additionally,  for $\cN(\mu, \sigma^2)$, Figure~\ref{fig:bias-variance-numerical} plots the characters featured in these decompositions $\hat \m_n^\text{MLE},\hat \m_n^\text{MAP},\m_n,\tilde \m_n, \m^*$ and $\m_0$ (and corresponding primal parameters) . \rlp{Tune figures.}\textcolor{red}{Not super clear, what is the "characters featured in these decompositions?"}

@@

\subsection{Gaussian Variance}
A core example is the centered Gaussian distribution with unknown variance $\cN(0,\sigma^2)$.
Its density reads 
\[
	p(x) = \inv{\sqrt{2\pi \sigma^2}} e^{-\frac{x^2}{2 \sigma^2}}.
\]
Defining $T(X)=X^2$ as the sufficient statistic, we get natural parameter $\nat = -\inv{2 \sigma^2} <0$, and mean parameter $\m=\E[T(X)] = \sigma^2 >0$.
Mean and natural parameters are roughly inverse of each other, i.e., $\nat = -\inv{2 \m}$.
\textcolor{red}{The explanation here is not clear enough, or too concise} Now we can match the log-likelihood with the exponential family template to get the log-partition function, and taking the conjugate to find the entropy
\begin{align}
	\logpart (\nat) &= - \half \log(-\nat)  + \half \log(\pi), \\
	\conj(\m) &= \half\left( -\log(\m) + \log\frac{\pi}{2} - 1 \right) \; .
\end{align}
Both the log-partition and  the entropy are roughly negative logarithm $z\mapsto - \log(z)$.
It means the conjugate prior is the exponential family with sufficient statistic $(\nat, \log(-\nat) )$, e.g., a negative Gamma distribution.
It also means $\bregman$ and $\bregmanconj$ have the same shape
\begin{align}
	\bregmanconj( \m_*; \m_n)
	&= \half \left ( \frac{\m_*}{ \m_n} - 1 - \log  \frac{\m_*}{ \m_n} \right), \\
	\bregman( \nat_n; \nat_* )
	&=  \half \left ( \frac{ \nat_n}{\nat_*} - 1 - \log  \frac{ \nat_n}{\nat_*} \right) \; .
\end{align}
Intuitively, the divergence measures the discrepancy between the ratio $\frac{ \nat_n}{\nat_*} =  \frac{\m_*}{ \m_n}  $ and $1$ via the function
\begin{align}
	\phi(z) := \half (z - 1 - \log(z))
\end{align}
illustrated in Figure~\ref{fig:phi}.

@@

Theorem \ref{eq:MLE_rate} reports upper bounds on the expected value of this divergence for the MLE and the MAP.

@@

For the MAP, we get an upper bound thanks to the inequality $ - \log(z) \leq \inv{z} - 1$, which implies
\begin{align}
	\label{eq:log_bound}
	\phi(z) \leq \half (z + \inv{z}) - 1 = \frac{(z-1)^2}{2 z} \; .
\end{align}

\begin{theorem}[MAP Bound]
For $n\in \naturalnumbers$, the expected suboptimality of the MAP of $\cN(0,\m^*)$ with prior hyper-parameters $(n_0,\m_0)$ is
 \begin{align}
	& \expect{\bregmanconj( \m_*; \hat \m_n^\mathrm{MAP})}
	\leq \begin{cases}
		\inv{2(n_0+1)}  +  b_1 \ \text{if}\ n=1,\\
		\frac{1}{n_0 \frac{\m_0}{\m^*} +n-2} + b_n \ \text{if}\ n\geq 2
	\end{cases}
	\label{eq:MAP_rate}\\
	& \text{where }b_n = \frac{(1 + \inv{n_0} - \frac{\m_0}{\m^*})^2}{2 (\frac{\m_0}{\m^*}+\frac{(n-2)_+}{n_0})(1 + \frac{n}{n_0} )} \; . \nonumber
\end{align}
\end{theorem}

This inequality highlights a clear variance-bias decomposition.
In particular, there is no bias term when $\frac{\m_0}{\m^*} =1 + \inv{n_0} $, which happens when the prior is slightly larger than the ground truth.  For instance, when $n_0=1$, it encourages us to set $\m_0 = 2 \m^*$. This correlates well with numerical observations.
Remark that the variance term is not asymptotically tight as the log-inequality we used \eqref{eq:log_bound} is not quadratically tight around $1$, therefore losing a factor 2 compared to $1/2n$.

@@

We now show how MAP can be interpreted as stochastic mirror descent (SMD).
This means that \textbf{1)} we may obtain a convergence rate for MAP from an optimization analysis, and \textbf{2)} any insights gained from the MAP may inform further design and analysis of SMD.
We then review the assumptions of relative smoothness, useful to deal with non-smooth functions, before investigating 3 analysis of SMD with the MAP.
\rlp{mention that examples have so far been lacking for relative SMD.}

@@

\subsubsection{Bounded Optimality Gap}
Inspired by \citet{loizou2021stochastic}, \citet{dorazio2021stochastic} explores the hypothesis
\alignn{
\min_\nat f(\nat) - \expect[X]{\min_\nat f_X(\nat)} \leq C 
\label{eq:dorazio}
}
where $f_X$ is a stochastic estimate of $f = \expecti{f_X}$. In our case $f_X(\nat) = - \log p(X\cond \nat)$.
In words, this is lower bounding the expectation of the minimum of these stochastic estimates.
For probabilistic models, such a bound is finite as soon as the model cannot give infinite density to any data point $x$.
This holds for instance for discrete distributions 
-- $f_x\geq 0$ because the probability mass is upper bounded by $1$ -- 
but it rules out  many families.
For normal distributions set $\mu=x$ and $\sigma^2 \rightarrow 0$ to get $p(x\cond \nat) \rightarrow +\infty$. 
For gamma, set $\alpha = \beta x$ and $beta \rightarrow +\infty$.
For beta, set $\alpha=\beta \frac{x}{1-x}$ and $\beta \rightarrow +\infty$.
 Other examples include inverse Gaussians, log-normal, gamma, inverse gamma.
